Deep mutational scanning of hemagglutinin helps predict evolutionary fates of human H3N2 influenza variants

### 2018-04-02 paper/manuscript.tex
Added PDF of frequency trajectory examples resized to fit in one column.
Updated WSN scatterplots for max frequency by mut effect.
Updated WSN histograms for max frequency by mut effect.

\begin{figure}[h!]
\centering
\includegraphics[width=\linewidth]{figs/frequency_trajectory_ex.png}
\caption{\label{fig:frequency_trajectory}
{\bf Frequency trajectories of individual mutations and their relation to the experimentally determined effects of these mutations.}
The top panel shows the subset of the full H3N2 HA tree in Figure~\ref{suppfig:tree} windowed from 2004 to 2014.
Circles indicate individual amino-acid mutations, and are colored according to the mutational effect measured in our deep mutational scanning (negative values indicate mutations measured to be deleterious to viral growth).
The bottom panel shows the frequency trajectory of each mutation, with mutation trajectories colored according to the mutational effects as in the top panel.
It is clear that most mutations that reach high frequency are measured to be relatively favorable in our experiments.
}
\end{figure}

@@

\begin{figure*}[ht]
\centering
\includegraphics[width=0.85\textwidth]{figs/muteffect_by_maxfreq_WSN_1.pdf}
\caption{\label{fig:muteffect_maxfreq_WSN}
{\bf Experimental measurements on an H1 HA are not informative about the evolutionary fate of H3N2 mutations.}
This figure repeats the analysis of the H3N2 mutation frequencies in Figure~\ref{fig:muteffect_maxfreq}A, but uses the deep mutational scanning data for an H1 HA as measured in \cite{doud2016accurate}, i.e.\
Figure~\ref{suppfig:muteffect_maxfreq_WSN_supp} shows the histograms comparable to those in Figure~\ref{fig:muteffect_maxfreq}B.
The empirical $P$-value represents the results of 1,000 permutations.
}
\end{figure*}

@@

\begin{suppfigure}[H]
\centerline{\includegraphics[width=0.75\textwidth]{figs/muteffect_by_maxfreq_WSN_2.pdf}}
\caption{\label{suppfig:muteffect_maxfreq_WSN_supp}
{\bf The distribution of mutational effects measured in H1 HA among H3N2 mutations binned by the maximum frequency that they reach.}
This figure repeats the analysis of the H3N2 mutation frequencies in Figure~\ref{fig:muteffect_maxfreq}B, but uses the deep mutational scanning data for an H1 HA as measured in \cite{doud2016accurate}.
}
\end{suppfigure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=\linewidth]{figs/frequency_trajectory_ex.pdf}
\caption{\label{fig:frequency_trajectory}
{\bf Frequency trajectories of individual mutations and their relation to the experimentally determined effects of these mutations.}
The top panel shows the subset of the full H3N2 HA tree in Figure~\ref{suppfig:tree} windowed from 2004 to 2014.
Circles indicate individual amino-acid mutations, and are colored according to the mutational effect measured in our deep mutational scanning (negative values indicate mutations measured to be deleterious to viral growth).
The bottom panel shows the frequency trajectory of each mutation, with mutation trajectories colored according to the mutational effects as in the top panel.
It is clear that most mutations that reach high frequency are measured to be relatively favorable in our experiments.
}
\end{figure}

@@

\begin{figure*}[ht]
\centering
\includegraphics[width=1.0\textwidth]{figs/muteffect_by_maxfreq_WSN_1.pdf}
\caption{\label{fig:muteffect_maxfreq_WSN}
{\bf Experimental measurements on an H1 HA are not informative about the evolutionary fate of H3N2 mutations.}
This figure repeats the analysis of the H3N2 mutation frequencies in Figure~\ref{fig:muteffect_maxfreq}A, but uses the deep mutational scanning data for an H1 HA as measured in \cite{doud2016accurate}, i.e.\
Figure~\ref{suppfig:muteffect_maxfreq_WSN_supp} shows the histograms comparable to those in Figure~\ref{fig:muteffect_maxfreq}B.
The empirical $P$-value represents the results of 1,000 permutations.
}
\end{figure*}

@@

\begin{suppfigure}[H]
\centerline{\includegraphics[width=1.0\textwidth]{figs/muteffect_by_maxfreq_WSN_2.pdf}}
\caption{\label{suppfig:muteffect_maxfreq_WSN_supp}
{\bf The distribution of mutational effects measured in H1 HA among H3N2 mutations binned by the maximum frequency that they reach.}
This figure repeats the analysis of the H3N2 mutation frequencies in Figure~\ref{fig:muteffect_maxfreq}B, but uses the deep mutational scanning data for an H1 HA as measured in \cite{doud2016accurate}.
}
\end{suppfigure}
